Supplementary material for ``Screening Sinkhorn Algorithm for regularized Optimal Transport''

### 2019-05-21 tex/v3/section_5_numeric_expes.tex
test

\begin{figure*}[t]
	\begin{center}
		\includegraphics[width=4.55cm]{../../figure/norm_M_Mu_marginals_toy_n1000} \hfill
		\includegraphics[width=4.55cm]{../../figure/norm_M_Mu_marginals_toy_n1000} \hfill
		\includegraphics[width=4.55cm]{../../figure/norm_M_time_toy_n1000}
	\end{center}
	\caption{Empirical evaluation of \emph{Screenkhorn} vs Sinkhorn for normalized cost matrix. (Top panel) marginal violations in relation with the budget of points and (Bottom panel) ratio of computation times $\frac{T_{\text{\emph{Screenkhorn}}}}{T_{\text{Sinkhorn}}}$. The results are averaged over 10 runs.} 
		\label{fig:margin_expe}
\end{figure*}

\emph{Screenkhorn} provides good approximation of the marginals $\mu$ and $\nu$ for ''high'' values of the regularization parameter $\eta$ ($\eta > 1$). The approximation quality diminishes for small $\eta$. As expected $\norm{{\mu} -{\mu}^{\text{sc}}}_1$ and $\norm{{\nu} -{\nu}^{\text{sc}}}_1$ converge to zero when increasing the budget of points. Remarkably those quantities are all almost null whatever the budget for high $\eta$.  According to computational gain, \emph{Screenkhorn} is, up to 2 times, faster than Sinkhorn at low budget $n_b/n$. The inverse situation occurs when $n_b/n$ gets close to 1. The computational benefit

>>>>

\begin{figure*}[t]
	\begin{center}
		\includegraphics[width=4.55cm]{../../figure/norm_M_Mu_marginals_toy_n1000} \hfill
		\includegraphics[width=4.55cm]{../../figure/norm_M_Mu_marginals_toy_n1000} \hfill
		\includegraphics[width=4.55cm]{../../figure/norm_M_time_toy_n1000}
	\end{center}
	\caption{Empirical evaluation of \emph{Screenkhorn} vs Sinkhorn for normalized cost matrix. (Top panel) marginal violations in relation with the budget of points and (Bottom panel) ratio of computation times $\frac{T_{\text{\emph{Screenkhorn}}}}{T_{\text{Sinkhorn}}}$. The results are averaged over 10 trials.} 
		\label{fig:margin_expe}
\end{figure*}

\emph{Screenkhorn} provides good approximation of the marginals $\mu$ and $\nu$ for ''high'' values of the regularization parameter $\eta$ ($\eta > 1$). The approximation quality diminishes for small $\eta$. As expected $\norm{{\mu} -{\mu}^{\text{sc}}}_1$ and $\norm{{\nu} -{\nu}^{\text{sc}}}_1$ converge to zero when increasing the budget of points. Remarkably those quantities are all almost null whatever the budget for high $\eta$.  According to computation gain, \emph{Screenkhorn} is, up to 2 times, faster than Sinkhorn at low budget $n_b/n$ while the reverse holds when $n_b/n$ gets close to 1.  Computational benefit of \emph{Screenkhorn} also depends on $\eta$ with appropriate values $\eta \leq 1$.
